Logistic Regression and SVM

### 2019-11-10 simple_ml/example/report2/paper.tex
start exp2.

% Define document title and author
	\title{Linear Regression, Ridge Regression \\and Gradient Descent}
	\maketitle

% Write abstract here
\begin{abstract}
In this report, we solve the house price prediction problem in Housing Dataset by using closed form solution (CFS) optimized linear regression (LR), CSF optimized ridge regression (RR), and LR optimized by Gradient Descent (GD) and its variants e.g. Stochastic Gradient Descent (SGD) and Mini Batch Gradient Descent (MBGD). \\
We perform experiments on four aspects: \\
1. Comparision between CFS optimized LR and CFS optimized RR. \\
2. Comparision between GD, SGD, MBGD in terms of convergence and time-cost. \\
3. Tuning learning rate in MBGD. \\
4. Comparision between CFS optimized and MBGD optimized LR. \\
\end{abstract}

>>>>

% Define document title and author
	\title{Logistic Regression and SVM}
	\maketitle

% Write abstract here
\begin{abstract}
In this report, we solve the binary classification problem in a9a Dataset by using Logistic Regression (LR) and Support Vector Machine (SVM). \\
We perform experiments on four aspects: \\
1. Comparision between CFS optimized LR and CFS optimized RR. \\
2. Comparision between GD, SGD, MBGD in terms of convergence and time-cost. \\
3. Tuning learning rate in MBGD. \\
4. Comparision between CFS optimized and MBGD optimized LR. \\
\end{abstract}
